Title

### 2014-07-18 paper.tex
added 図

\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

Wow. This is just a placeholder text. Since this data is a great contribution to our research, I will cite their paper three times: [1][1][1].
TODO(get rid of this joke and this paragraph altogether, and replace with the actual overview of the method).

\subsection{The Data Set}

@@

% quick structure
Each change includes a \emph{commit message} which describes what is changed.
After a change is submitted to Gerrit, reviewers can give scores to it.
The scores will determine whether the change will be accepted or not.
Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.

@@

The commit messages and all comment texts are converted into vectors as part of the preparation step.
We wrote scripts in Ruby language to perform these tasks.

>>>>

\graphicspath{{zu/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\hyphenation{op-tical net-works semi-conduc-tor}

@@

@@

% quick structure
Each change includes a \emph{commit message} which describes what is changed.
After a change is submitted to Gerrit, reviewers can give scores to it.
The scores will determine whether the change will be accepted or not.
Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.
In this paper, we use the term \emph{document} to refer to a single commit message or comment.
Fig. \ref{fig:hierarchy} shows the relation between documents.

\begin{figure}
\centering
\includegraphics[width=2.5in]{hierarchy}
\caption{Relationship between documents.
Each rectangle represents a document, which may either be a commit message or a comment.}
\label{fig:hierarchy}
\end{figure}

@@

The commit messages and all comment texts are converted into vectors as part of the preparation step.
Fig. \ref{fig:preprocess} illustrates the overview of this step.
We wrote scripts in Ruby language to perform these tasks.

\begin{figure}
\centering
\includegraphics[width=2.5in]{preprocess}
\caption{The data preparation process.
Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
and are converted into a vector.}
\label{fig:preprocess}
\end{figure}
